### 2022-06-02 chapters/fairness/fif/experiments.tex
tables and figures updated with short caption

\begin{figure}[!t]
	\begin{minipage}{0.49\textwidth}
		\centering
		\subfloat[Statistical parity]{\includegraphics[scale=0.39]{figures/fairness/fif/sp_train_accuracy}}
	\end{minipage}
	\begin{minipage}{0.5\textwidth}
		\centering
		\subfloat[Equalized odds]{\includegraphics[scale=0.39]{figures/fairness/fif/eo_train_accuracy}}
	\end{minipage}
	\caption{Comparing {\fairXplainer} and SHAP on the estimation error of fairness metrics. Lower values on the $ Y $-axis denote a better result. {\fairXplainer} has significantly less error than SHAP.}\label{fig:estimation_error}
%	\vspace{-0.5em}
\end{figure}
\noindent\textbf{Accurate Estimation of Bias.} We compare {\fairXplainer} with SHAP in estimating Statistical Parity $(\mathsf{SP})$ and Equalized Odds $(\mathsf{EO})$, where each metric is calculated by summing all FIFs (Axiom~\ref{axm:additivity}). We consider five datasets, each trained on different classifiers by applying five-fold cross-validation. We compute estimation error by taking the absolute difference between the exact and  estimated value of a metric, and present results in Figure~\ref{fig:estimation_error}. In both metrics, {\fairXplainer} demonstrates significantly less error than SHAP. For example, the mean error of {\fairXplainer} in estimating $ \mathsf{SP} $ on Titanic dataset is $ 0.1 $ vs.\ $ 0.42 $ for SHAP. In this context, the error of {\fairXplainer} is often zero in most datasets and only insignificant ($ \le 0.13 $) due to the degenerate cases (Section~\ref{sec:fifs}) with $ \Pr[\widehat{Y} = 1 | \sensitive = \mathbf{a}] \in \{0, 1\} $.  Therefore, \emph{global sensitivity analysis based approach {\fairXplainer} is significantly more accurate in computing FIFs and corresponding fairness metric than local explanation based approach SHAP}.

@@

\noindent\textbf{Individual vs.\ Intersectional FIFs.} Now, we aim to understand the importance of intersectional FIFs over individual FIFs. We consider COMPAS dataset with race = \{Caucasian, non-Caucasian\} as the sensitive feature, and a logistic regression classifier to predict whether a person will re-offend crimes within the next two years. Since the classifier only optimizes training error, it demonstrates statistical parity as $ 0.17 $, which means a non-Caucasian  has $ 0.17 $ higher probability of re-offending crimes than a Caucasian. Next, we investigate the source of bias and present individual FIFs in Figure~\ref{fig:individual_fifs}, and both individual and intersectional FIFs in Figure~\ref{fig:individual_and_intersectional_fifs}. In both figures, we show top seven influential FIFs sorted by absolute values,  followed by residual higher-order FIFs. In Figure~\ref{fig:individual_fifs}, `priors count' of an individual is dominating in increasing statistical parity (FIF $ = 0.12 $). Other non-sensitive features appear to have almost zero FIFs. However, the sum of second-order influences of all features increases statistical parity by $ 0.06 $, denoting that the data is highly correlated and presenting only individual FIFs does not trace the true sources of bias. For example, while both `sex' and `age' of persons have zero influence on bias (Figure~\ref{fig:individual_fifs}), these features together with `c charge degree', `priors count', and `juvenile other count' contribute highly on statistical parity (sum of FIFs $ = 0.03 + 0.02 + 0.01 + 0.01 - 0.01 - 0.01 = 0.05$). \emph{Therefore, intersectional influences together with individual influences lead to a clearer understanding on the source of bias of a classifier. Note that, unlike SHAP, {\fairXplainer} is the only framework that computes beyond individual FIFs.}
\begin{figure}[t!]
	\begin{minipage}{0.43\textwidth}
		\centering
		\subfloat[Individual FIFs]{\includegraphics[scale=0.35]{figures/fairness/fif/feature_weight_unsorted}\label{fig:individual_fifs}}
	\end{minipage}
	\begin{minipage}{0.5\textwidth}
		\centering
		\subfloat[Individual and intersectional FIFs]{\includegraphics[scale=0.35]{figures/fairness/fif/feature_weight}\label{fig:individual_and_intersectional_fifs}}
	\end{minipage}
	\vspace{-0.2em}
	\caption{FIFs for COMPAS dataset on explaining statistical parity. Intersectional FIFs depict sources of bias in detail than individual FIFs.}\label{fig:individual_vs_intersectional_influence}

\end{figure}
\begin{figure}[t!]
	\vspace{-0.7em}
	\begin{minipage}{0.49\textwidth}
		\centering
		\subfloat[Fairness attack (punitive actions)]{\includegraphics[scale=0.345]{figures/fairness/fif/fairness_attack}\label{fig:fairness_attack}}
	\end{minipage}
	\begin{minipage}{0.5\textwidth}
		\centering	
		\subfloat[Fairness enchancing algorithm (affirmative actions)]{\includegraphics[scale=0.345]{figures/fairness/fif/fairness_repair}\label{fig:fairness_repair}}
	\end{minipage}
	\vspace{-0.2em}
	\caption{Effects of a fairness attack~\cite{solans2020poisoning} and a fairness enhancing algorithm~\cite{kamiran2012data} on FIFs.}\label{fig:affirmative_punitive_actions}
%	\vspace{-0.5em}
\end{figure}

>>>>

\begin{figure}[!t]
	\begin{minipage}{0.49\textwidth}
		\centering
		\subfloat[Statistical parity]{\includegraphics[scale=0.39]{figures/fairness/fif/sp_train_accuracy}}
	\end{minipage}
	\begin{minipage}{0.5\textwidth}
		\centering
		\subfloat[Equalized odds]{\includegraphics[scale=0.39]{figures/fairness/fif/eo_train_accuracy}}
	\end{minipage}
	\caption[Accuracy of {\fairXplainer}]{Comparing {\fairXplainer} and SHAP on the estimation error of fairness metrics. Lower values on the $ Y $-axis denote a better result. {\fairXplainer} has significantly less error than SHAP.}\label{fig:estimation_error}
%	\vspace{-0.5em}
\end{figure}
\noindent\textbf{Accurate Estimation of Bias.} We compare {\fairXplainer} with SHAP in estimating Statistical Parity $(\mathsf{SP})$ and Equalized Odds $(\mathsf{EO})$, where each metric is calculated by summing all FIFs (Axiom~\ref{axm:additivity}). We consider five datasets, each trained on different classifiers by applying five-fold cross-validation. We compute estimation error by taking the absolute difference between the exact and  estimated value of a metric, and present results in Figure~\ref{fig:estimation_error}. In both metrics, {\fairXplainer} demonstrates significantly less error than SHAP. For example, the mean error of {\fairXplainer} in estimating $ \mathsf{SP} $ on Titanic dataset is $ 0.1 $ vs.\ $ 0.42 $ for SHAP. In this context, the error of {\fairXplainer} is often zero in most datasets and only insignificant ($ \le 0.13 $) due to the degenerate cases (Section~\ref{sec:fifs}) with $ \Pr[\widehat{Y} = 1 | \sensitive = \mathbf{a}] \in \{0, 1\} $.  Therefore, \emph{global sensitivity analysis based approach {\fairXplainer} is significantly more accurate in computing FIFs and corresponding fairness metric than local explanation based approach SHAP}.

@@

\noindent\textbf{Individual vs.\ Intersectional FIFs.} Now, we aim to understand the importance of intersectional FIFs over individual FIFs. We consider COMPAS dataset with race = \{Caucasian, non-Caucasian\} as the sensitive feature, and a logistic regression classifier to predict whether a person will re-offend crimes within the next two years. Since the classifier only optimizes training error, it demonstrates statistical parity as $ 0.17 $, which means a non-Caucasian  has $ 0.17 $ higher probability of re-offending crimes than a Caucasian. Next, we investigate the source of bias and present individual FIFs in Figure~\ref{fig:individual_fifs}, and both individual and intersectional FIFs in Figure~\ref{fig:individual_and_intersectional_fifs}. In both figures, we show top seven influential FIFs sorted by absolute values,  followed by residual higher-order FIFs. In Figure~\ref{fig:individual_fifs}, `priors count' of an individual is dominating in increasing statistical parity (FIF $ = 0.12 $). Other non-sensitive features appear to have almost zero FIFs. However, the sum of second-order influences of all features increases statistical parity by $ 0.06 $, denoting that the data is highly correlated and presenting only individual FIFs does not trace the true sources of bias. For example, while both `sex' and `age' of persons have zero influence on bias (Figure~\ref{fig:individual_fifs}), these features together with `c charge degree', `priors count', and `juvenile other count' contribute highly on statistical parity (sum of FIFs $ = 0.03 + 0.02 + 0.01 + 0.01 - 0.01 - 0.01 = 0.05$). \emph{Therefore, intersectional influences together with individual influences lead to a clearer understanding on the source of bias of a classifier. Note that, unlike SHAP, {\fairXplainer} is the only framework that computes beyond individual FIFs.}
\begin{figure}[t!]
	\begin{minipage}{0.43\textwidth}
		\centering
		\subfloat[Individual FIFs]{\includegraphics[scale=0.35]{figures/fairness/fif/feature_weight_unsorted}\label{fig:individual_fifs}}
	\end{minipage}
	\begin{minipage}{0.5\textwidth}
		\centering
		\subfloat[Individual and intersectional FIFs]{\includegraphics[scale=0.35]{figures/fairness/fif/feature_weight}\label{fig:individual_and_intersectional_fifs}}
	\end{minipage}
	\vspace{-0.2em}
	\caption[Individual vs.\ intersectional FIFs]{FIFs for COMPAS dataset on explaining statistical parity. Intersectional FIFs depict sources of bias in detail than individual FIFs.}\label{fig:individual_vs_intersectional_influence}

\end{figure}
\begin{figure}[t!]
	\vspace{-0.7em}
	\begin{minipage}{0.49\textwidth}
		\centering
		\subfloat[Fairness attack (punitive actions)]{\includegraphics[scale=0.345]{figures/fairness/fif/fairness_attack}\label{fig:fairness_attack}}
	\end{minipage}
	\begin{minipage}{0.5\textwidth}
		\centering	
		\subfloat[Fairness enchancing algorithm (affirmative actions)]{\includegraphics[scale=0.345]{figures/fairness/fif/fairness_repair}\label{fig:fairness_repair}}
	\end{minipage}
	\vspace{-0.2em}
	\caption[FIFs under fairness attack and fairness enhancing algorithms]{Effects of a fairness attack~\cite{solans2020poisoning} and a fairness enhancing algorithm~\cite{kamiran2012data} on FIFs.}\label{fig:affirmative_punitive_actions}
%	\vspace{-0.5em}
\end{figure}

### 2022-06-02 chapters/fairness/fif/figure_intro.tex
tables and figures updated with short caption

	\caption{FIFs of input features to investigate the bias (i.e., statistical parity) of a decision tree classifier predicting the eligibility for health insurance using age-dependent features `fitness' and `income'. An affirmative action reduces bias, and corresponding FIFs present the evidence.}
	\label{fig:fair_example_fif}
	\vspace{-1em}
\end{figure}

>>>>

	\caption[Illustration of fairness influence functions]{FIFs of input features to investigate the bias (i.e., statistical parity) of a decision tree classifier predicting the eligibility for health insurance using age-dependent features `fitness' and `income'. An affirmative action reduces bias, and corresponding FIFs present the evidence.}
	\label{fig:fair_example_fif}
	\vspace{-1em}
\end{figure}

### 2022-06-02 chapters/fairness/fvgm/applications.tex
tables and figures updated with short caption

\begin{figure}
	\centering
	\subfloat{\includegraphics[scale=0.2]{figures/fairness/fvgm/disp_fairness_attack}}
	\subfloat{\includegraphics[scale=0.2]{figures/fairness/fvgm/stat_fairness_attack}}

	\captionof{figure}{Verifying poisoning attack against fairness using {\fvgm}. The red line denotes the safety margin of the ML model against the attack.}\label{fvgm_fig:fairness_attacks}
\end{figure}

@@

\begin{figure}[t!]	
	\centering
	\vspace{-2ex}
	\subfloat{\includegraphics[scale=0.23]{figures/fairness/fvgm/dependency_exp_Learn-dependency_compas_lr_sex_1}}
	\subfloat{\includegraphics[scale=0.23]{figures/fairness/fvgm/dependency_exp_Learn-dependency_compas_lr_sex_0}}
	%\vspace{-0.5em}
%	\vspace{-2ex}
	\caption{FIF computation for COMPAS dataset. For Female (left plot) and Male, influence of `age' decreases and the probability of positive prediction of the classifier increases  by different magnitudes.}\label{fvgm_fig:influence function}
%	\vspace{-2ex}
\end{figure}

>>>>

\begin{figure}
	\centering
	\subfloat{\includegraphics[scale=0.3]{figures/fairness/fvgm/disp_fairness_attack}}
	\subfloat{\includegraphics[scale=0.3]{figures/fairness/fvgm/stat_fairness_attack}}

	\caption[Verifying fairness attacks]{Verifying poisoning attack against fairness using {\fvgm}. The red line denotes the safety margin of the ML model against the attack.}\label{fvgm_fig:fairness_attacks}
\end{figure}

@@

\begin{figure}[t!]	
	\centering
	\vspace{-2ex}
	\subfloat{\includegraphics[scale=0.3]{figures/fairness/fvgm/dependency_exp_Learn-dependency_compas_lr_sex_1}}
	\subfloat{\includegraphics[scale=0.3]{figures/fairness/fvgm/dependency_exp_Learn-dependency_compas_lr_sex_0}}
	%\vspace{-0.5em}
%	\vspace{-2ex}
	\caption[FIF computation using {\fvgm}]{FIF computation for COMPAS dataset. For Female (left plot) and Male, influence of `age' decreases and the probability of positive prediction of the classifier increases  by different magnitudes.}\label{fvgm_fig:influence function}
%	\vspace{-2ex}
\end{figure}

### 2022-06-02 chapters/fairness/fvgm/dp_illustration.tex
tables and figures updated with short caption

\caption{Search tree representation of {\stochastic} for computing the maximum probability of positive prediction of the classifier on variables $ \mathbf{B} =  \{P,Q,R,S\} $ with weights $ \{1,1,1,-1\} $ and threshold $ \tau = 2 $ . Each node is labeled by $ (i,\tau') $, where $ i $ is the index of $ \mathbf{B} $ and $ \tau' $ is the residual threshold. The tree is explored using Depth-First Search (DFS) starting with left child. Within a node, the value in the bottom denotes $ \mathsf{dp}(i, \tau') $ that is solved recursively based on sub-problems $ \mathsf{dp}(i+1, \cdot) $ in child nodes. 	Yellow nodes denote \textit{existential} variables and all other nodes are  \textit{random} variables. Additionally, a green node denotes a collision, in which case a previously computed $ \mathsf{dp} $ solution is returned. Leaf nodes (gray) are computed based on terminating conditions in Eq.~\eqref{fvgm_eq:dp_terminus}. In Figure~\ref{fvgm_fig:example_BN},  nodes with double circles, such as $ \{(1,2), (2,1), (2,2)\} $,  are enumerated exponentially to compute conditional probabilities from the Bayesian network.}
\label{fvgm_fig:example_tree_exploration}
\end{figure*}

>>>>

\caption[Simulation of stochastic subset-sum problem]{Search tree representation of {\stochastic} for computing the maximum probability of positive prediction of the classifier on variables $ \mathbf{B} =  \{P,Q,R,S\} $ with weights $ \{1,1,1,-1\} $ and threshold $ \tau = 2 $ . Each node is labeled by $ (i,\tau') $, where $ i $ is the index of $ \mathbf{B} $ and $ \tau' $ is the residual threshold. The tree is explored using Depth-First Search (DFS) starting with left child. Within a node, the value in the bottom denotes $ \mathsf{dp}(i, \tau') $ that is solved recursively based on sub-problems $ \mathsf{dp}(i+1, \cdot) $ in child nodes. 	Yellow nodes denote \textit{existential} variables and all other nodes are  \textit{random} variables. Additionally, a green node denotes a collision, in which case a previously computed $ \mathsf{dp} $ solution is returned. Leaf nodes (gray) are computed based on terminating conditions in Eq.~\eqref{fvgm_eq:dp_terminus}. In Figure~\ref{fvgm_fig:example_BN},  nodes with double circles, such as $ \{(1,2), (2,1), (2,2)\} $,  are enumerated exponentially to compute conditional probabilities from the Bayesian network.}
\label{fvgm_fig:example_tree_exploration}
\end{figure*}

### 2022-06-02 chapters/fairness/fvgm/evaluations.tex
tables and figures updated with short caption

\begin{figure}[t!]
	\begin{center}		
		\subfloat{\includegraphics[scale=0.24]{figures/fairness/fvgm/cactus_all_verifiers_LR_time_}}\\
		\subfloat{\includegraphics[scale=0.24]{figures/fairness/fvgm/cactus_all_verifiers_SVM_time_}}		
	\end{center}
	%	\vspace{-2ex}
	\caption{A cactus plot to present the scalability of different fairness verifiers. The number of solved benchmarks are on the $ X $-axis and the required time is on the $ Y $-axis; a point $ (x,y) $ implies that a verifier takes less than or equal to $ y $ seconds to compute fairness metrics of $ x $ many benchmarks. We consider $ 100 $ benchmarks generated from $ 5 $ real-world datasets using $ 5 $-fold cross-validation. In each fold, we consider $\{25, 50, 75, 100\} $ percent of non-sensitive features.}\label{fvgm_fig:scalability_exp}
	%	\vspace{-2ex}
\end{figure}

@@

\begin{figure}[t!]
	\begin{center}	
		\subfloat{\includegraphics[scale=0.24]{figures/fairness/fvgm/sanity_DI_LR_01}}\\
		\subfloat{\includegraphics[scale=0.24]{figures/fairness/fvgm/sanity_DI_SVM_01}}		
		%		\subfloat[]{\includegraphics[scale=0.25]{figures/fairness/fvgm/sanity_DI_LR_005}}
		%		\subfloat[]{\includegraphics[scale=0.25]{figures/fairness/fvgm/sanity_DI_SVM_005}}
		%				
	\end{center}
	%	\vspace{-2ex}
	\caption{Comparing the average accuracy of different verifiers over 100 synthetic benchmarks while varying the number of features. {\fvgm} yields the closest estimation of the analytically calculated \textit{Exact} values of DI for LR and SVM classifiers.}\label{fvgm_fig:sanity_exp}
	%	\vspace{-2ex}
\end{figure}
\subsection{Accuracy Analysis}
\noindent\textbf{Benchmark Generation.} To perform accuracy analysis, we require the ground truth, which is not available for real-world instances. Therefore, we focus on generating synthetic benchmarks for analytically computing the ground truth of different fairness metrics, such as DI, from the known distribution of features. In each benchmark, we consider $ n \in \{2, 3, 4, 5\} $ features including one Boolean sensitive feature, say $ A $, generated from a Bernoulli distribution with mean $ 0.5 $.  We generate non-sensitive features $ X_i $ from Gaussian distributions such that   $ \Pr[X_i | A = 1] \sim \mathcal{N}(\mu_i, \sigma^2) $ and $ \Pr[X_i | A = 0] \sim \mathcal{N}(\mu_i', \sigma^2) $, where $ \mu_i, \mu_i' \in [0,1] $, $ \sigma = 0.1 $, and $ \mu_i, \mu_i' $ are chosen from a uniform distribution in $ [0,1] $. Finally, we create label $ Y = \mathds{1}[ \sum_{i=1}^{n-1} X_i \ge 0.5 \sum_{i=1}^{n-1} (\mu_i + \mu_i')] $ such that $ Y $ does not directly depend on the sensitive feature. For each $ n $, we generate $ 100 $ random benchmarks, learn LR and SVM classifiers on them, and compute DI\footnote{  
To analytically compute DI, let the coefficients of the classifier be $ w_i $ for $ X_i $ and $ w_A $ for $ A $, and bias be $ \tau $. Since all non-sensitive features are from Gaussian distributions, we compute the probability of the predicted class $ \Pr[\hat{Y} | A = 1]  \sim \mathcal{N}(\sum_{i=1}^{n-1}w_i\mu_i, \sigma_{\hat{Y}}^2) $ and $ \Pr[\hat{Y} | A = 0]  \sim \mathcal{N}(\sum_{i=1}^{n-1}w_i\mu_i', \sigma_{\hat{Y}}^2) $ with $ \sigma_{\hat{Y}}^2 =   (\sum_{i=1}^{n-1}w_i^2)\sigma^2 $. Hence, the probability of positive prediction of the classifier  is $  1 - \mathsf{CDF}_{\hat{Y}| A =1}(\tau - w_A) $ for $ A = 1 $ and $  1 - \mathsf{CDF}_{\hat{Y}|A=0}(\tau) $ for $ A = 0 $, where $ \mathsf{CDF} $ is the cumulative distribution function. Finally, we compute DI by taking the ratio of the minimum and the maximum of the probability of positive prediction of the classifier.}
using different verifiers.

@@

\begin{table}[!t]
		\centering

		\setlength{\tabcolsep}{0.45em}
		\begin{tabular}{lllrrrrrrrrrrrrr}

@@

	\caption{Verification of fairness algorithms using {\fvgm}. $ \sensitive $ denotes sensitive features.  RW and OP refer to reweighing and optimized-preprocessing algorithms. Numbers in bold refer to fairness improvement.   }\label{fvgm_tab:fair_algo_verification}

>>>>

\begin{figure}[t!]
	\begin{center}		
		\subfloat{\includegraphics[scale=0.3]{figures/fairness/fvgm/cactus_all_verifiers_LR_time_}}
		\subfloat{\includegraphics[scale=0.3]{figures/fairness/fvgm/cactus_all_verifiers_SVM_time_}}		
	\end{center}
	%	\vspace{-2ex}
	\caption[Scalability of {\fvgm}]{A cactus plot to present the scalability of different fairness verifiers. The number of solved benchmarks are on the $ X $-axis and the required time is on the $ Y $-axis; a point $ (x,y) $ implies that a verifier takes less than or equal to $ y $ seconds to compute fairness metrics of $ x $ many benchmarks. We consider $ 100 $ benchmarks generated from $ 5 $ real-world datasets using $ 5 $-fold cross-validation. In each fold, we consider $\{25, 50, 75, 100\} $ percent of non-sensitive features.}\label{fvgm_fig:scalability_exp}
	%	\vspace{-2ex}
\end{figure}

@@

\begin{figure}[t!]
	\begin{center}	
		\subfloat{\includegraphics[scale=0.3]{figures/fairness/fvgm/sanity_DI_LR_01}}
		\subfloat{\includegraphics[scale=0.3]{figures/fairness/fvgm/sanity_DI_SVM_01}}		
		%		\subfloat[]{\includegraphics[scale=0.25]{figures/fairness/fvgm/sanity_DI_LR_005}}
		%		\subfloat[]{\includegraphics[scale=0.25]{figures/fairness/fvgm/sanity_DI_SVM_005}}
		%				
	\end{center}
	%	\vspace{-2ex}
	\caption[Accuracy of {\fvgm}]{Comparing the average accuracy of different verifiers over 100 synthetic benchmarks while varying the number of features. {\fvgm} yields the closest estimation of the analytically calculated \textit{Exact} values of DI for LR and SVM classifiers.}\label{fvgm_fig:sanity_exp}
	%	\vspace{-2ex}
\end{figure}
\subsection{Accuracy Analysis}
\noindent\textbf{Benchmark Generation.} To perform accuracy analysis, we require the ground truth, which is not available for real-world instances. Therefore, we focus on generating synthetic benchmarks for analytically computing the ground truth of different fairness metrics, such as DI, from the known distribution of features. In each benchmark, we consider $ n \in \{2, 3, 4, 5\} $ features including one Boolean sensitive feature, say $ A $, generated from a Bernoulli distribution with mean $ 0.5 $.  We generate non-sensitive features $ X_i $ from Gaussian distributions such that   $ \Pr[X_i | A = 1] \sim \mathcal{N}(\mu_i, \sigma^2) $ and $ \Pr[X_i | A = 0] \sim \mathcal{N}(\mu_i', \sigma^2) $, where $ \mu_i, \mu_i' \in [0,1] $, $ \sigma = 0.1 $, and $ \mu_i, \mu_i' $ are chosen from a uniform distribution in $ [0,1] $. Finally, we create label $ Y = \mathds{1}[ \sum_{i=1}^{n-1} X_i \ge 0.5 \sum_{i=1}^{n-1} (\mu_i + \mu_i')] $ such that $ Y $ does not directly depend on the sensitive feature. For each $ n $, we generate $ 100 $ random benchmarks, learn LR and SVM classifiers on them, and compute DI\footnote{  
To analytically compute DI, let the coefficients of the classifier be $ w_i $ for $ X_i $ and $ w_A $ for $ A $, and bias be $ \tau $. Since all non-sensitive features are from Gaussian distributions, we compute the probability of the predicted class $ \Pr[\hat{Y} | A = 1]  \sim \mathcal{N}(\sum_{i=1}^{n-1}w_i\mu_i, \sigma_{\hat{Y}}^2) $ and $ \Pr[\hat{Y} | A = 0]  \sim \mathcal{N}(\sum_{i=1}^{n-1}w_i\mu_i', \sigma_{\hat{Y}}^2) $ with $ \sigma_{\hat{Y}}^2 =   (\sum_{i=1}^{n-1}w_i^2)\sigma^2 $. Hence, the probability of positive prediction of the classifier  is $  1 - \mathsf{CDF}_{\hat{Y}| A =1}(\tau - w_A) $ for $ A = 1 $ and $  1 - \mathsf{CDF}_{\hat{Y}|A=0}(\tau) $ for $ A = 0 $, where $ \mathsf{CDF} $ is the cumulative distribution function. Finally, we compute DI by taking the ratio of the minimum and the maximum of the probability of positive prediction of the classifier.}
using different verifiers.

@@

\begin{table}[!t]

	\caption[Verification of fairness metrics and algorithms using {\fvgm}]{Verification of fairness algorithms using {\fvgm}. $ \sensitive $ denotes sensitive features.  RW and OP refer to reweighing and optimized-preprocessing algorithms. Numbers in bold refer to fairness improvement.   }\label{fvgm_tab:fair_algo_verification}

		\centering

%		\setlength{\tabcolsep}{0.45em}
		\begin{tabular}{lllrrrrrrrrrrrrr}

@@

### 2022-06-02 chapters/fairness/fvgm/introduction.tex
tables and figures updated with short caption

%KSM: Make the two plots side by side
\begin{figure}[h!]
	%		{r}{0.25\textwidth}%\vspace*{-2.4em}
	\begin{center}
		\includegraphics[scale = 0.4]{figures/fairness/fvgm/sanity_probability}
	\end{center}
%	\vspace*{-1em}
	\caption{Age-dependent distributions of income and fitness in Example~\ref{fvgm_example:intro}.}\label{fvgm_fig:example1}%\vspace*{-1.6em}
\end{figure}

>>>>

%KSM: Make the two plots side by side
\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale = 0.5]{figures/fairness/fvgm/sanity_probability}
	\end{center}
	\caption[Illustrative distribution of features]{Age-dependent distributions of income and fitness in Example~\ref{fvgm_example:intro}.}\label{fvgm_fig:example1}
\end{figure}

### 2022-06-02 chapters/fairness/justicia/experiments.tex
tables and figures updated with short caption

\begin{figure*}
	\centering
	\subfloat{
		\includegraphics[scale=.2]{figures/fairness/justicia/sensitive_attribute_race_di_Adult_DT_RE.pdf}
	}
	\subfloat{
		\includegraphics[scale=.2]{figures/fairness/justicia/sensitive_attribute_race_spd_Adult_DT_RE.pdf}
	}
	\caption{Fairness metrics measured by {\justicia} for different sensitive groups in the Adult dataset. The number within parenthesis in the xticks denotes total compound groups.}
	\label{fairness_justicia_fig:sensitive_groups}
\end{figure*}

@@

\begin{figure*}
	\centering
	\subfloat{\includegraphics[scale=.2]{figures/fairness/justicia/sampling_DI_after_Adult_rw_LR_race.pdf}}
	\subfloat{\includegraphics[scale=.2]{figures/fairness/justicia/sampling_SPD_after_Adult_rw_LR_race.pdf}}		\caption{Standard deviation in estimation of disparate impact (DI) and stat. parity (SP)  for different sample sizes (sample size $ = 1 $ refers to the entire dataset). {\justicia} is more robust with variation of sample size than  AIF360. }
	\label{fairness_justicia_fig:sample-size}
\end{figure*}

\begin{figure}[t!]
	\begin{center}
		\includegraphics[scale=.4]{figures/fairness/justicia/encoding_runtime_Adult_DT.pdf}
		\includegraphics[scale=.4]{figures/fairness/justicia/encoding_runtime_Adult_IMLI.pdf}
		\hfill
		\caption{Runtime comparison of different encodings while varying total sensitive groups in the Adult dataset. \red{Label `learn' to be `infer'???}}
		\label{fairness_justicia_fig:runtime_diff_encodings}
	\end{center}
\end{figure}

>>>>

\begin{figure*}
	\centering
	\subfloat{
		\includegraphics[scale=.2]{figures/fairness/justicia/sensitive_attribute_race_di_Adult_DT_RE.pdf}
	}
	\subfloat{
		\includegraphics[scale=.2]{figures/fairness/justicia/sensitive_attribute_race_spd_Adult_DT_RE.pdf}
	}
	\caption[Fairness verification on compound sensitive groups]{Fairness metrics measured by {\justicia} for different sensitive groups in the Adult dataset. The number within parenthesis in the xticks denotes total compound groups.}
	\label{fairness_justicia_fig:sensitive_groups}
\end{figure*}

@@

\begin{figure*}
	\centering
	\subfloat{\includegraphics[scale=.2]{figures/fairness/justicia/sampling_DI_after_Adult_rw_LR_race.pdf}}
	\subfloat{\includegraphics[scale=.2]{figures/fairness/justicia/sampling_SPD_after_Adult_rw_LR_race.pdf}}

	\caption[Robustness of fairness verification]{Standard deviation in estimation of disparate impact (DI) and stat. parity (SP)  for different sample sizes (sample size $ = 1 $ refers to the entire dataset). {\justicia} is more robust with variation of sample size than  AIF360. }
	\label{fairness_justicia_fig:sample-size}
\end{figure*}

\begin{figure}[t!]
	\begin{center}
		\includegraphics[scale=.4]{figures/fairness/justicia/encoding_runtime_Adult_DT.pdf}
		\includegraphics[scale=.4]{figures/fairness/justicia/encoding_runtime_Adult_IMLI.pdf}
		\hfill
		\caption[Runtime of different encodings in {\justicia}]{Runtime comparison of different encodings while varying total sensitive groups in the Adult dataset. \red{Label `learn' to be `infer'???}}
		\label{fairness_justicia_fig:runtime_diff_encodings}
	\end{center}
\end{figure}
